%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english,russian]{babel} % added russian
\usepackage{tabularx}
\usepackage{calc} % added
\usepackage{ragged2e}

\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheadingLeftOneRow}[2]{% % added
  \begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
  \end{description}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge Aleksandr Nelzin} \\ \vspace{2pt}
    \small +77073571374 $|$ \href{mailto:asnelzin@gmail.com}{\underline{asnelzin@gmail.com}} $|$
    \href{https://linkedin.com/in/asnelzin}{\underline{linkedin.com/in/asnelzin}} $|$
    \href{https://github.com/asnelzin}{\underline{github.com/asnelzin}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Senior Software Engineer}{November 2018 -- Present}
      {Togezzer.net, Inc.}{Remote, USA}
      \resumeItemListStart
        \resumeItem{Handled both software engineering and infrastructure responsibilities, actively participated in creating product requirements and architecture.}
        \resumeItem{Contributed to over 50 new product features, including core functionalities like tasks, projects, and more.}
        \resumeItem{Optimized automated testing, reducing the overall quality assurance cycle time by 30\%.}
        \resumeItem{Designed and implemented a new payment subsystem from scratch, integrating 2 payment providers, enabling seamless transactions for users.}
        \resumeItem{Integrated over 5 third-party services in response to user feature requests.}
        \resumeItem{Completely rewrote the authentication subsystem from legacy Tarantool database to PostgreSQL, leading to 20\% faster response times and 50\% faster development cycles.}
      \resumeItemListEnd

  \resumeSubheading
      {Software Engineer}{April 2018 -- October 2018}
      {Mail.ru Group}{Saint Petersburg, Russia}
      \resumeItemListStart
        \resumeItem{Contributed to the development and launch of over 5 new projects, including initial discussions on business requirements, architecture design, development, and testing.}
        \resumeItem{Implemented over 3 integrations with other company projects, such as video calls, monitoring, and analytics.}
        \resumeItem{Conducted code reviews and mentored junior developers, fostering a collaborative environment.}
        \resumeItem{Participated in planning and retrospective meetings, helping improve team productivity by 20\%.}
      \resumeItemListEnd

  \resumeSubheading
      {Software Engineer}{July 2017 -- April 2018}
      {ESforce Holding}{Saint Petersburg, Russia}
      \resumeItemListStart
        \resumeItem{Participated in early-stage development of a microservices backend for the video streaming service Looch.tv, developing over 2 microservices from scratch and supporting 10 existing ones.}
        \resumeItem{Developed a service for real-time video stream recording from scratch, enhancing user experience.}
        \resumeItem{Created unit and integration tests to maintain code quality.}
        \resumeItem{Performed program profiling and load testing to ensure system reliability and scalability.}
      \resumeItemListEnd

  \resumeSubheading
      {Software Engineer}{May 2016 -- June 2017}
      {SputnikMobile}{Saint Petersburg, Russia}
      \resumeItemListStart
        \resumeItem{Developed web services for the American market, specifically a service for identifying key moments in video recordings of team sports, including football, basketball, and rugby.}
      \resumeItemListEnd

  % \resumeSubheading
  %     {QA Engineer}{November 2014 -- May 2016}
  %     {Netrika}{Saint Petersburg, Russia}
  %     \resumeItemListStart
  %       \resumeItem{Performed both manual and automated testing, ensuring product quality.}
  %       \resumeItem{Wrote and maintained testing tools for continuous integration/continuous deployment (CI/CD) using Jenkins.}
  %       \resumeItem{Set up and maintained CI/CD pipelines, improving team efficiency.}
  %     \resumeItemListEnd

  % \resumeSubheading
  %     {Intern Software Engineer}{July 2014 -- August 2014}
  %     {Netrika}{Saint Petersburg, Russia}
  %     \resumeItemListStart
  %       \resumeItem{Participated in the development and testing of several projects using Django as part of a collaborative team of developers.}
  %     \resumeItemListEnd

  % \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {ITMO University}{September 2011 -- July 2015}
      {Bachelor of Science in Engineering, Specialization: Mechatronics and Robotics}{Saint Petersburg, Russia}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Go, Python, SQL} \\
     \textbf{Frameworks}{: aiohttp, Django, FastAPI} \\
     \textbf{Databases}{: PostgreSQL, Redis, SQLite, BoltDB, MongoDB}\\
     \textbf{Architecture}{: REST, gRPC, Microservices}\\
     \textbf{Distributed Systems}{: RabbitMQ, Apache Kafka}\\
     \textbf{Development Tools}{: Git, Makefile, Prometheus, Grafana, Loki, nginx} \\
     \textbf{CI/CD, Cloud}{: GitLab CI/CD, Drone CI, Docker, Kubernetes, AWS}\\
    }}
 \end{itemize}

%-----------LANGUAGES-----------
\section{Language Proficiency}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{: Upper-intermediate (B2)} \\
     \textbf{Russian}{: Native}
    }}
 \end{itemize}

\end{document}
